Data_cleaning

### 2021-07-02 1_cleaning.Rmd
cleaning of code

ind <-
  read.dta13("1_country_data/ind/IGC_vacstudy_blfu12.dta", 
             nonint.factors = TRUE) %>%
  dplyr::as_tibble() %>% 
  dplyr::filter(!is.na(vac1)) %>% 
  dplyr::rename(
    age = HH_age,
    gender = HH_sex,
    take_vaccine = vac1) %>%
  dplyr::mutate(
    w_id=paste0(slum_code, hhid),
    study = "ind_igc",
    educ = ifelse(hhb_hh_head_educs == 1, "More than secondary", NA_character_),
    educ = ifelse(hhb_hh_head_educs == 0, "Less than secondary", educ),
    gender = as.factor(gender),
    gender = recode(gender, 
                    "1" = "Male", 
                    "0" = "Female"), 
    take_vaccine = recode(take_vaccine, 
                          "Yes, only for free" = "Yes", 
                          "Yes, even if I have to pay" = "Yes")) %>%
  dplyr::select(w_id, survey_date,
                study, age, gender, educ, take_vaccine, 
                starts_with("trust_vaccine_"), weight = pweight, cluster = slum_code) %>%
  dplyr::mutate(across(c(starts_with("trust_vaccine"), weight), ~ replace(., is.na(.), 0)))

@@

ind <- ind %>%
  mutate(date=lubridate::mdy(survey_date)) %>%
  group_by(w_id) %>%
  slice(which.max(date)) %>%
  left_join(ind_avg)

@@

pak_2 <- 
  read.dta13("1_country_data/pak_2/CERP_EVA_Data.dta") %>%
  filter(resp_province=="Punjab") %>%
  dplyr::as_tibble() %>% 
  dplyr::mutate(
    educ = recode(i_0, 
                  "Refused to answer" = NA_character_,
                  "Did not go to school" = "Less than secondary",
                  "Dropped out before Matric" = "Less than secondary",
                  "Matric" = "Secondary",
                  "Intermediate/ F.A/ FS.c" = "More than secondary",
                  "Bachelors" = "More than secondary",
                  "Masters/Mphil/ M.Ed" = "More than secondary",
                  "Phd" = "More than secondary",
                  "Religious Studies" = "Less than secondary",
                  "Vocational training/Diploma/D.A.E" = "More than secondary"),
    take_vaccine = recode(s7_10, 
                          "Absolutely yes" = "Yes",
                          "Absolutely no" = "No",
                          "Neutral" = "DK"),
    study = "pak_igc2") %>%
  dplyr::select(
    study, educ, take_vaccine, 
    starts_with(c("yes_vaccine", "no_vaccine", "trust_vaccine_")))

@@

      ifelse(trust_vaccine == "Friends you see and talk to" | trust_vaccine == "Friends you’ve made online", 1, 0),

@@

  read.dta13("1_country_data/sle_1/SLE_vaccine_data.dta",

@@

  as_tibble() %>% 

@@

  read.dta13("1_country_data/sle_2/vaccine_subset.dta",

@@

      ifelse(trust_vaccine == "A doctor, nurse or other staff at a community health clinic" |

@@

uga_1 <-  
  read.dta13("1_country_data/uga/IGC_Covid19vaccine_questions_final_clusterID.dta",
             nonint.factors = FALSE, generate.factors = TRUE) %>%
  dplyr::as_tibble() %>% 
  dplyr::rename(
    take_vaccine = vacc_yn,
    age = current_age) %>%
  dplyr::mutate(
    study = "uga_igc",
    no_vaccine_1 = ifelse(vacc_why_no_1 == 1, 1, 0),
    no_vaccine_3 = ifelse(vacc_why_no_2 == 1, 1, 0),
    no_vaccine_4 = ifelse(vacc_why_no_3 == 1, 1, 0),
    no_vaccine_5 = ifelse(vacc_why_no_4 == 1, 1, 0),
    no_vaccine_6 = ifelse(vacc_why_no_5 == 1, 1, 0),
    no_vaccine_8 = ifelse(vacc_why_no_6 == 1, 1, 0),
    no_vaccine_666 = ifelse(vacc_why_no_7 == 1 | vacc_why_no__66 == 1, 1, 0),
    yes_vaccine_1 = ifelse(vacc_why_yes_1 == 1, 1, 0),
    yes_vaccine_2 = ifelse(vacc_why_yes_2 == 1, 1, 0),
    yes_vaccine_3 = ifelse(vacc_why_yes_3 == 1, 1, 0),
    yes_vaccine_5 = ifelse(vacc_why_yes_5 == 1, 1, 0),
    yes_vaccine_666 = ifelse(vacc_why_yes_4 == 1, 1, 0),
    yes_vaccine_666 = ifelse(vacc_why_yes__66 == 1, 1, yes_vaccine_666),
    educ = ifelse(respondent_educ <= 8, "Less than secondary", NA_character_),
    educ = ifelse(respondent_educ <= 14 & respondent_educ > 8, "Secondary", educ),
    educ = ifelse(respondent_educ > 14, "More than secondary", educ),
    gender = as.factor("Female")) %>%
  dplyr::select(
    study, age, gender, educ, take_vaccine, 
    starts_with(c("yes_vaccine", "no_vaccine", "trust_vaccine_")), 
    cluster = clusterID) %>%
  dplyr::mutate(across(c(yes_vaccine_1:no_vaccine_666), ~replace(., is.na(.), 0)))

@@

load("1_country_data/usa/usa_covid_survey.RData")
usa <- 
  d %>%
  dplyr::as_tibble() %>% 
  dplyr::select(
    gender, age, starts_with("WZB"), weight = weights, edu) %>%
  dplyr::mutate(
    yes_vaccine_1 = as.numeric(WZB_yes_vaccine_1),
    yes_vaccine_2 = as.numeric(WZB_yes_vaccine_2),
    yes_vaccine_3 = as.numeric(WZB_yes_vaccine_3),
    yes_vaccine_5 = as.numeric(WZB_yes_vaccine_4),
    take_vaccine = ifelse(WZB_take_vaccine == 2 | WZB_take_vaccine == 1, "Yes", WZB_take_vaccine),
    take_vaccine = ifelse(take_vaccine == -1 | take_vaccine == -2, "No", take_vaccine),
    take_vaccine = ifelse(take_vaccine == -99, NA_character_, take_vaccine),
    no_vaccine_1 = ifelse(WZB_no_vaccine_1 == 1, 1, 0),
    no_vaccine_3 = ifelse(WZB_no_vaccine_2 == 1, 1, 0),
    no_vaccine_4 = ifelse(WZB_no_vaccine_3 == 1, 1, 0),
    no_vaccine_9 = ifelse(WZB_no_vaccine_conspiracy == 1, 1, 0),
    no_vaccine_666 = 
      ifelse(WZB_no_vaccine_4 == 1 | WZB_no_vaccine_text_code %in% c("2", "5", "11", "3, 11", "888"),1,0),
    trust_vaccine_1 = ifelse(WZB_trust_vaccine == 1, 1, 0),
    trust_vaccine_3 = ifelse(WZB_trust_vaccine == 8, 1, 0),
    trust_vaccine_5 = ifelse(WZB_trust_vaccine == 2 , 1, 0),
    trust_vaccine_6 = ifelse(WZB_trust_vaccine == 3 | WZB_trust_vaccine == 4 | 
                               WZB_trust_vaccine == 6 | WZB_trust_vaccine == 7, 1, 0),
    trust_vaccine_nr = ifelse(WZB_trust_vaccine == -99, 1, 0),
    trust_vaccine_other = ifelse(WZB_trust_vaccine == 5, 1, 0),
    trust_vaccine_666 = ifelse(WZB_trust_vaccine == 9, 1, 0),
    gender = recode(gender, 
                    "1" = "Male", 
                    "2" = "Female"),
    educ = ifelse(edu > 2 | edu == -99, "More than secondary", "Secondary"),
    age = as.integer(age),
    study = "usa_wzb") %>%
  dplyr::select(
    study, age, gender, educ, take_vaccine, 
    starts_with(c("yes_vaccine", "no_vaccine", "trust_vaccine_")), 
    weight) %>%
  dplyr::mutate(across(c(yes_vaccine_1:trust_vaccine_666), ~replace(., is.na(.), 0)))

@@

df <- 
  dfs %>% 
  plyr::llply(
    .data = .,
    .fun = function(df) {
      if (!is.null(df$cluster)) df %<>% mutate(cluster = as.character(cluster))
      return(df)
    }
  ) %>% 
  dplyr::bind_rows() %>% 
  dplyr::left_join(dplyr::select(studies, study, country), by = "study") %>%
  dplyr::mutate(
    take_vaccine_num = ifelse(take_vaccine == "Yes", 1, 0),
    take_vaccine_num = ifelse(is.na(take_vaccine), 0, take_vaccine_num),
    take_vaccine_num = ifelse(study=="ind_igc", mean, take_vaccine_num),
    cluster = 
      ifelse(is.na(cluster), NA, 
             paste0(gsub(pattern = " ", replacement = "_", x = tolower(country)), "_", cluster))) %>%
  dplyr::select(any_of(vars))

@@

readr::write_csv(table_wgm, "3_rep_data/table_wgm.csv")
```

@@

readr::write_csv(vacc_cov, "3_rep_data/vacc_cov.csv")
```

>>>>

ind <-
  read.dta13("1_country_data/ind/IGC_vacstudy_blfu12.dta", 
             nonint.factors = TRUE) %>%
  dplyr::as_tibble() %>% 
  dplyr::filter(!is.na(vac1)) %>% 
  dplyr::rename(
    age = HH_age,
    gender = HH_sex,
    take_vaccine = vac1) %>%
  dplyr::mutate(
    w_id = paste0(slum_code, hhid),
    study = "ind_igc",
    educ = ifelse(hhb_hh_head_educs == 1, "More than secondary", NA_character_),
    educ = ifelse(hhb_hh_head_educs == 0, "Less than secondary", educ),
    gender = as.factor(gender),
    gender = recode(gender, 
                    "1" = "Male", 
                    "0" = "Female"), 
    take_vaccine = recode(take_vaccine, 
                          "Yes, only for free" = "Yes", 
                          "Yes, even if I have to pay" = "Yes")) %>%
  dplyr::select(w_id, survey_date,
                study, age, gender, educ, take_vaccine, 
                starts_with("trust_vaccine_"), weight = pweight, cluster = slum_code) %>%
  dplyr::mutate(across(c(starts_with("trust_vaccine"), weight), ~ replace(., is.na(.), 0)))

@@

ind <- ind %>%
  mutate(date = lubridate::mdy(survey_date)) %>%
  group_by(w_id) %>%
  slice(which.max(date)) %>%
  left_join(ind_avg)

@@

pak_2 <- 
  read.dta13("1_country_data/pak_2/CERP_EVA_Data.dta") %>%
  filter(resp_province == "Punjab") %>%
  dplyr::as_tibble() %>% 
  dplyr::mutate(
    educ = recode(i_0, 
                  "Refused to answer" = NA_character_,
                  "Did not go to school" = "Less than secondary",
                  "Dropped out before Matric" = "Less than secondary",
                  "Matric" = "Secondary",
                  "Intermediate/ F.A/ FS.c" = "More than secondary",
                  "Bachelors" = "More than secondary",
                  "Masters/Mphil/ M.Ed" = "More than secondary",
                  "Phd" = "More than secondary",
                  "Religious Studies" = "Less than secondary",
                  "Vocational training/Diploma/D.A.E" = "More than secondary"),
    take_vaccine = recode(s7_10, 
                          "Absolutely yes" = "Yes",
                          "Absolutely no" = "No",
                          "Neutral" = "DK"),
    study = "pak_igc2") %>%
  dplyr::select(
    study, educ, take_vaccine, 
    starts_with(c("yes_vaccine", "no_vaccine", "trust_vaccine_")))

@@

@@

  readstata13::read.dta13(
    file = "1_country_data/sle_1/SLE_vaccine_data.dta",

@@

@@

  readstata13::read.dta13(
    file = "1_country_data/sle_2/vaccine_subset.dta",

@@

    trust_vaccine_5 = ifelse(
      trust_vaccine == "A doctor, nurse or other staff at a community health clinic" |

@@

uga_1 <-  
  readstata13::read.dta13(
    file = "1_country_data/uga/IGC_Covid19vaccine_questions_final_clusterID.dta",
    nonint.factors = FALSE, generate.factors = TRUE) %>%
  dplyr::as_tibble() %>% 
  dplyr::rename(
    take_vaccine = vacc_yn,
    age = current_age) %>%
  dplyr::mutate(
    study = "uga_igc",
    no_vaccine_1 = ifelse(vacc_why_no_1 == 1, 1, 0),
    no_vaccine_3 = ifelse(vacc_why_no_2 == 1, 1, 0),
    no_vaccine_4 = ifelse(vacc_why_no_3 == 1, 1, 0),
    no_vaccine_5 = ifelse(vacc_why_no_4 == 1, 1, 0),
    no_vaccine_6 = ifelse(vacc_why_no_5 == 1, 1, 0),
    no_vaccine_8 = ifelse(vacc_why_no_6 == 1, 1, 0),
    no_vaccine_666 = ifelse(vacc_why_no_7 == 1 | vacc_why_no__66 == 1, 1, 0),
    yes_vaccine_1 = ifelse(vacc_why_yes_1 == 1, 1, 0),
    yes_vaccine_2 = ifelse(vacc_why_yes_2 == 1, 1, 0),
    yes_vaccine_3 = ifelse(vacc_why_yes_3 == 1, 1, 0),
    yes_vaccine_5 = ifelse(vacc_why_yes_5 == 1, 1, 0),
    yes_vaccine_666 = ifelse(vacc_why_yes_4 == 1, 1, 0),
    yes_vaccine_666 = ifelse(vacc_why_yes__66 == 1, 1, yes_vaccine_666),
    educ = ifelse(respondent_educ <= 8, "Less than secondary", NA_character_),
    educ = ifelse(respondent_educ <= 14 & respondent_educ > 8, "Secondary", educ),
    educ = ifelse(respondent_educ > 14, "More than secondary", educ),
    gender = as.factor("Female")) %>%
  dplyr::select(
    study, age, gender, educ, take_vaccine, 
    starts_with(c("yes_vaccine", "no_vaccine", "trust_vaccine_")), 
    cluster = clusterID) %>%
  dplyr::mutate(across(c(yes_vaccine_1:no_vaccine_666), ~replace(., is.na(.), 0)))

@@

load("1_country_data/usa/usa_covid_survey.RData")
usa <- 
  d %>%
  dplyr::as_tibble() %>% 
  dplyr::select(
    gender, age, starts_with("WZB"), weight = weights, edu) %>%
  dplyr::mutate(
    yes_vaccine_1 = as.numeric(WZB_yes_vaccine_1),
    yes_vaccine_2 = as.numeric(WZB_yes_vaccine_2),
    yes_vaccine_3 = as.numeric(WZB_yes_vaccine_3),
    yes_vaccine_5 = as.numeric(WZB_yes_vaccine_4),
    take_vaccine = ifelse(WZB_take_vaccine == 2 | WZB_take_vaccine == 1, "Yes", WZB_take_vaccine),
    take_vaccine = ifelse(take_vaccine == -1 | take_vaccine == -2, "No", take_vaccine),
    take_vaccine = ifelse(take_vaccine == -99, NA_character_, take_vaccine),
    no_vaccine_1 = ifelse(WZB_no_vaccine_1 == 1, 1, 0),
    no_vaccine_3 = ifelse(WZB_no_vaccine_2 == 1, 1, 0),
    no_vaccine_4 = ifelse(WZB_no_vaccine_3 == 1, 1, 0),
    no_vaccine_9 = ifelse(WZB_no_vaccine_conspiracy == 1, 1, 0),
    no_vaccine_666 = 
      ifelse(WZB_no_vaccine_4 == 1 | 
               WZB_no_vaccine_text_code %in% c("2", "5", "11", "3, 11", "888"), 1, 0),
    trust_vaccine_1 = ifelse(WZB_trust_vaccine == 1, 1, 0),
    trust_vaccine_3 = ifelse(WZB_trust_vaccine == 8, 1, 0),
    trust_vaccine_5 = ifelse(WZB_trust_vaccine == 2 , 1, 0),
    trust_vaccine_6 = ifelse(WZB_trust_vaccine == 3 | WZB_trust_vaccine == 4 | 
                               WZB_trust_vaccine == 6 | WZB_trust_vaccine == 7, 1, 0),
    trust_vaccine_nr = ifelse(WZB_trust_vaccine == -99, 1, 0),
    trust_vaccine_other = ifelse(WZB_trust_vaccine == 5, 1, 0),
    trust_vaccine_666 = ifelse(WZB_trust_vaccine == 9, 1, 0),
    gender = recode(gender, 
                    "1" = "Male", 
                    "2" = "Female"),
    educ = ifelse(edu > 2 | edu == -99, "More than secondary", "Secondary"),
    age = as.integer(age),
    study = "usa_wzb") %>%
  dplyr::select(
    study, age, gender, educ, take_vaccine, 
    starts_with(c("yes_vaccine", "no_vaccine", "trust_vaccine_")), 
    weight) %>%
  dplyr::mutate(across(c(yes_vaccine_1:trust_vaccine_666), ~replace(., is.na(.), 0)))

@@

df <- 
  dfs %>% 
  plyr::llply(
    .data = .,
    .fun = function(df) {
      if (!is.null(df$cluster)) df %<>% mutate(cluster = as.character(cluster))
      return(df)
    }
  ) %>% 
  dplyr::bind_rows() %>% 
  dplyr::left_join(dplyr::select(studies, study, country), by = "study") %>%
  dplyr::mutate(
    take_vaccine_num = ifelse(take_vaccine == "Yes", 1, 0),
    take_vaccine_num = ifelse(is.na(take_vaccine), 0, take_vaccine_num),
    take_vaccine_num = ifelse(study == "ind_igc", mean, take_vaccine_num),
    cluster = 
      ifelse(is.na(cluster), NA, 
             paste0(gsub(pattern = " ", replacement = "_", x = tolower(country)), "_", cluster))) %>%
  dplyr::select(any_of(vars))

@@

readr::write_csv(table_wgm, "3_rep_data/table_wgm.csv")

@@

readr::write_csv(vacc_cov, "3_rep_data/vacc_cov.csv")
